\documentclass[12pt,a4paper]{article}
\usepackage[top=1in, bottom=1in, left=1.25in, right=0.75in]{geometry}
\usepackage{mdwlist}
\usepackage{hyperref}
\usepackage{url}
\usepackage{setspace}
\usepackage{amsmath,amsthm,amssymb}
\hypersetup{colorlinks=false,pdfborder={0 0 0}}
\begin{document}
\newpage
\thispagestyle{empty}
\section{Abstract}
\doublespacing

	\ \ \ \ Sudoku is a number placement puzzle which requires logic to solve. The objective is to fill 9x9 grid such that each row, each coloumn, and each 3x3 sub-grid to get values from 1-9 without repetition. i.e., no value can be repeated in the same row, same column and same box (3x3 grid). Many solutions to SuDokus are available such as \textit{backtracking technique} and \textit{brute fore technique}. In the technique discussed, a \textit{mathematical apporach} is given to solve sudoku using \textit{SET theory operations}. Set data structure and associated Set operations such as \textit{Union, Intersection and Difference} are implemented using \textit{BitVectors} and will help in reducing space and time complexity.

\newpage
\thispagestyle{empty}

\section{Acknowledgements}

\ \ \ \ My sincere regards to \textbf{Dr. B. G. Sangameshwara}, \textit{Principal of S.J.C.E} for providing me an opportunity to enhance my knowledge by working on this seminar. I also would like to thank \textbf{Dr. C.N. Ravikumar}, Professor and \textit{Head of department of Computer science and Engineering} for the implementation of plan of the seminar in our curriculum to enhance the knowledge and communication skills of the students. I am especially grateful to my guide \textbf{Smt. M. A. Anusuya} \textit{Assistant Professor, department of Computer science and Engineering} for her exemplary guidance, monitoring and constant encouragement throughout the course of carrying out this seminar.  I also thank my \textbf{Parents} and \textit{Friends} who have constantly supported me in all ways possible.

\vspace{10cm} 
\begin{flushright}
Pradeep Kashyap R.\\
8$^{th}$ sem\\
Dept. of CS \& E\\
SJCE, Mysore\\
\end{flushright}


\end{document}

